### 2021-04-14 Chapter-5/Chapter-5.tex
Updates from Overleaf

\textbf{Benchmark}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{2}{c}{\textbf{\# Leaked Functions}} & \multicolumn{2}{c}{\textbf{Max. Leak (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{3}{c}{\textbf{Performance}}    \\ 
\cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-12}& \# & bits &  1 Byte &  64 Bytes & 1 Byte  & 64 Bytes & LoC & Size & Fuzzing & Comparison & Chi-squared
\\\midrule
Unsafe Password Checker& 65536& 16.0& 1&0&0.04&  0& 18 & 104 KB & 21 min & 0.4 min & 0 min\\
Safe Password Checker & 65536 & 16.0& 0&0 &0 &0 & 20 & 106 KB & 20 min & 0.4 min & 0 min\\
One-byte Lookup Table & 65536 & 16.0& 1&1&9.8& 3.6 & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
Four-byte Lookup Table & 65536 & 16.0& 1&1&9.6& 8.5 & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
AES T-Table mbedTLS 2.15 & 65536 & 16.0&2&2&11.6 &6.7& -& 1.1 MB &65 min & 0.8 min & 0.1 min  \\
AES NI mbedTLS 2.15 & 65536 & 16.0&0&0&0 &0&-& 1.1 MB & 45 min & 0 min & 0 min  \\
AES OpenSSL 1.1.0  & 65536 & 16.0 & 2&0 &1.4 & 0&-& 1.0 MB  & 49 min & 0.2 min & 0 min \\
AES  OpenSSL 1.1.1& 65536 & 16.0 & 2&0 &1.3&0&-& 909 KB & 46 min & 0.2 min & 0 min\\
AES  wolfSSL 4.5.0& 65536 & 16.0 &2&0& 0.11& 0 & - &1.1 MB & 53 min & 0.1 min & 0 min \\
AES Libgcrypt 1.8.7& 65536 & 16.0 &0 &0 &0&0 &-&4.4 MB & 164 min& 0 min & 0 min\\
RSA mbedTLS 2.15& 4096 & 12.0 &10&8&13.3& 6.0 &-&1.8 MB\\
RSA OpenSSL 1.1.0& 4096 & 12.0 &14&6&6.7& 4.1 &-& 11 MB\\
RSA OpenSSL 1.1.1& 4096 & 12.0 &6&4&6.3& 2.1&&13 MB\\
RSA wolfSSL 4.5.0& 4096 & 12.0 &5&2&3.4& 2.5&&4.2 MB\\
RSA Libgcrypt 1.8.7& 4096 & 12.0 &8&6&8.6& 6.6&&4.4 MB\\
Tiny DNN & 12000 & - & 17&14&17.1&16.1&-& 4.4 MB \\
GDK 3.24.23 & 65535 & 16.0 & 33&31& 12.1& 6.0&-& 48 MB\\
\bottomrule
\end{tabular}
}

>>>>

\textbf{Benchmark}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{2}{c}{\textbf{\# Leaked Functions}} & \multicolumn{2}{c}{\textbf{Max. Leak (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{3}{c}{\textbf{Performance}}    \\ 
\cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-12}& \# & bits &  1 Byte &  64 Bytes & 1 Byte  & 64 Bytes & LoC & Size & Fuzzing & Comparison & Chi-squared
\\\midrule
Unsafe Password Checker& 65536& 16.0& 1&0&0.04&  0& 18 & 104 KB & 21 min & 0.4 min & 0 min\\
Safe Password Checker & 65536 & 16.0& 0&0 &0 &0 & 20 & 106 KB & 20 min & 0.4 min & 0 min\\
One-byte Lookup Table & 65536 & 16.0& 1&1&9.8& 3.6 & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
Four-byte Lookup Table & 65536 & 16.0& 1&1&9.6& 8.5 & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
AES T-Table mbedTLS 2.15 & 65536 & 16.0&2&2&11.6 &6.7& -& 1.1 MB &65 min & 0.8 min & 0.1 min  \\
AES NI mbedTLS 2.15 & 65536 & 16.0&0&0&0 &0&-& 1.1 MB & 45 min & 0 min & 0 min  \\
AES OpenSSL 1.1.0  & 65536 & 16.0 & 2&0 &1.4 & 0&-& 1.0 MB  & 49 min & 0.2 min & 0 min \\
AES  OpenSSL 1.1.1& 65536 & 16.0 & 2&0 &1.3&0&-& 909 KB & 46 min & 0.2 min & 0 min\\
AES  wolfSSL 4.5.0& 65536 & 16.0 &2&0& 0.11& 0 & - &1.1 MB & 53 min & 0.1 min & 0 min \\
AES Libgcrypt 1.8.7& 65536 & 16.0 &0 &0 &0&0 &-&4.4 MB & 164 min& 0 min & 0 min\\
RSA mbedTLS 2.15& 4096 & 12.0 &10&8&13.3& 6.0 &-&1.8 MB\\
RSA OpenSSL 1.1.0& 4096 & 12.0 &14&6&6.7& 4.1 &-& 11 MB\\
RSA OpenSSL 1.1.1& 4096 & 12.0 &6&4&6.3& 2.1&-&13 MB\\
RSA wolfSSL 4.5.0& 4096 & 12.0 &5&2&3.4& 2.5&-&4.2 MB\\
RSA Libgcrypt 1.8.7& 4096 & 12.0 &8&6&8.6& 6.6&-&4.4 MB\\
Tiny DNN & 12000 & - & 17&14&17.1&16.1&-& 4.4 MB \\
GDK 3.24.23 & 65535 & 16.0 & 33&31& 12.1& 6.0&-& 48 MB\\
\bottomrule
\end{tabular}
}
